---
title: "hakim2017"
author: "anjie"
date: "4/9/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)

d <- read_csv(here("data/All_Data_Coded.csv")) 
```
Hakim, N., Simons, D. J., Zhao, H., & Wan, X. (2017). Do easterners and westerners differ in visual cognition? A preregistered examination of three visual cognition tasks. Social Psychological and Personality Science, 8(2), 142-152.

## descriptive 
> Eastern and Western participants, our final sample included fewer Asians (n 1⁄4 72) than Americans (n 1⁄4 95). 

```{r}
d %>%
  filter(Exclude_too_long_in_West != 1) %>% 
  group_by(East_or_West) %>% 
  count()
```
## color detection task 


> dPrimeExpand <- qnorm(ExpandHitRate) - qnorm(ExpandFARate)
	dPrimeContract <- qnorm(ContractHitRate) - qnorm(ContractFARate)
	dprimeExpandMinusContract <- dPrimeExpand - dPrimeContract
	dprimeExpandContractMean <- (dPrimeExpand + dPrimeContract)/2
	


```{r}
d_color <- d %>% 
  filter(ExpandContractExclude == 0) %>% 
  select(SubNum, East_or_West, starts_with("dPrime"), starts_with("expand")) %>% 
  select(SubNum, 
         East_or_West, 
         dPrime_Expand, dPrime_Contract,
         Expand_Minus_Contract_dPrime, Expand_Contract_Mean_dPrime) %>% 
  rename(dPrime_Expand_Minus_Contract = Expand_Minus_Contract_dPrime, 
         dPrime_Expand_Contract_Mean = Expand_Contract_Mean_dPrime) %>% 
  pivot_longer(
    cols = c(dPrime_Expand, dPrime_Contract, dPrime_Expand_Minus_Contract), 
    names_to = "dprime_type", 
    values_to = "dprime_value"
  )


d_color
```

```{r}
d_color %>% 
  mutate(
    culture_print = case_when(
      East_or_West == "e" ~ "Asian International", 
      East_or_West == "w" ~ "American", 
      East_or_West == "c" ~ "Chinese"
    )
  ) %>% 
  filter(dprime_type == "dPrime_Expand_Minus_Contract") %>% 
  ggplot(aes(x = culture_print, y = dprime_value)) + 
  geom_violin() + 
   geom_point(alpha = .3) + 
  stat_summary(fun.data = "mean_cl_boot", colour = "red")+
  scale_y_continuous(breaks = seq(-2, 5, 0.5)) + 
  facet_wrap(~fct_rev(dprime_type)) + 
  theme_classic()

d_color %>% 
  mutate(
    culture_print = case_when(
      East_or_West == "e" ~ "Asian International", 
      East_or_West == "w" ~ "American", 
      East_or_West == "c" ~ "Chinese"
    )
  ) %>% 
  filter(dprime_type != "dPrime_Expand_Minus_Contract") %>% 
  ggplot(aes(x = culture_print, y = dprime_value)) + 
  geom_violin() + 
   geom_point(alpha = .3) + 
  stat_summary(fun.data = "mean_cl_boot", colour = "red")+
  scale_y_continuous(breaks = seq(-2, 5, 0.5)) + 
  facet_wrap(~fct_rev(dprime_type)) + 
  theme_classic()

```

